Welfare Expectations Across U.S. Economic Cycles

### 2024-04-24 paper/paper.qmd
Update caption for figures

```{r}
#| warning: false
#| fig-cap: Trend of Average Inapplicable Responses Per Decade is increasing
#| label: fig-inapplicable-years
#| message: false
#| echo: false

>>>>

```{r}
#| warning: false
#| fig-cap: Trend of Average Inapplicable Responses Per Decade is Increasing
#| label: fig-inapplicable-years
#| message: false
#| echo: false
